Compositional equivalences based on Open pNets

### 2020-06-03 2016-Weak-FH-Bisim/WeakBisim.tex
abstract

This article defines bisimulation relations for the pNet model, to compare  systems described using the pNets model.
 We define a strong bisimulation for open pNets.
  In practice, as happens in process algebras, strong bisimulation is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.
  We then define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties.

Amon these properties we show compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.

  Which significant (small) use-case ?

\end{abstract}

\maketitle

\section*{Status and TODO list}

TODOS: AVRIL 2019

- exemple (Eric: failure buffer)
- biblio (rabea)
- inuitions de preuves et intuition de bisim de cloture, etc. (Ludo)

%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}

%% \TODO{prendre soin des posts sur les actions partout}

%% ===> dealine 14 Juillet

%% TODOs du 19 decembre

%% - enlever 5.2 et citer avocs

%% - ajouter des proof sketch dans le papier

%% - def 11 point 2:
%% A, Pred, Post
%% -----------   in T
%% s->s'
%% et A(j)=tau
%% implies blablabla

%% OLD OLD OLD (check)
%% Notes de reunion 24 Sept

%% - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif

%% - target: JLamp

%% Conventions
%% [14/9/2018]

%% Dans le texte pas de $\backslash$ devant pNet et pLTS

%% pNet devient P ou Q dans les equations; on garde $pLTS$

%% \medskip

%% TODOS et deadline

%% Global and questions:
%% \begin{itemize}
%% \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
%% \item related works
%% \end{itemize}
%% Ludo:
%% \begin{itemize}
%% \item[X] reorga sec weak bisim + thm -> 10 Juil
%% \item[X]  intro et orga globale du papier -> fin aout
%% \item[partial] explication dans semantique open pnets et composition
%% \item uniformisation pNet P Q
%% \end{itemize}

>>>>

This article defines bisimulation relations for the pNet modelfor the comparison of systems specified as pNets.
 We first define a strong bisimulation for open pNets.
  In practice, as happens in process algebras, strong bisimulation is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.
  We then define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties.
Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
The article is illustrated with a running example showing the characteristics of our formalism and our bisimulation relations.
\end{abstract}

\maketitle
%
%\section*{Status and TODO list}
%
%TODOS: AVRIL 2019
%
%- exemple (Eric: failure buffer)
%- biblio (rabea)
%- inuitions de preuves et intuition de bisim de cloture, etc. (Ludo)
%
%%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
%
%%% \TODO{prendre soin des posts sur les actions partout}
%
%%% ===> dealine 14 Juillet
%
%%% TODOs du 19 decembre
%
%
%
%%% - enlever 5.2 et citer avocs
%
%%% - ajouter des proof sketch dans le papier
%
%%% - def 11 point 2:
%%% A, Pred, Post
%%% -----------   in T
%%% s->s'
%%% et A(j)=tau
%%% implies blablabla
%
%
%%% OLD OLD OLD (check)
%%% Notes de reunion 24 Sept
%
%
%%% - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
%
%
%
%%% - target: JLamp
%
%%% Conventions
%%% [14/9/2018] 
%
%%% Dans le texte pas de $\backslash$ devant pNet et pLTS
%
%%% pNet devient P ou Q dans les equations; on garde $pLTS$
%
%%% \medskip
%
%%% TODOS et deadline
%
%
%%% Global and questions:
%%% \begin{itemize}
%%% \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
%%% \item related works
%%% \end{itemize}
%%% Ludo:
%%% \begin{itemize}
%%% \item[X] reorga sec weak bisim + thm -> 10 Juil
%%% \item[X]  intro et orga globale du papier -> fin aout
%%% \item[partial] explication dans semantique open pnets et composition
%%% \item uniformisation pNet P Q
%%% \end{itemize}
%
%
